A Random Choice SPH Scheme with Adaptive Viscosity

### 2018-06-07 ebp-JCPManuscript.tex
abani+ebp cleans

\modulolinenumbers[5]
\journal{Journal of Computational Physics}
%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%
%% Numbered
\bibliographystyle{model1-num-names}
%% Numbered without titles
%\bibliographystyle{model1a-num-names}
%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}
%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}
%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}
%% `Elsevier LaTeX' style
%\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{frontmatter}
\title{IA Random Choice SPH Scheme with Adaptive Viscosity}
%\tnotetext[mytitlenote]{Can add  title note here}
%% Group authors per affiliation:
\author{Zhixuan Cao}
\author{Abani Patra \fnref{mycorrespondingauthor}}
\address{Department of Mechanical and Aerospace Engineering,The State University of New York at Buffalo, Amherst, NY, 14260-4200, USA}
\author{E. Bruce Pitman}
\address{Department of Materials Design and Innovation, The State University of New York at Buffalo, Amherst, NY, 14260-4200, USA}
%\fntext[myfootnote]{Since 1880.}
%% or include affiliations in footnotes:
%\author[mymainaddress,mysecondaryaddress]%{Elsevier Inc}
%\ead[url]{www.elsevier.com}
%\author[mysecondaryaddress]{Global Customer Service\corref{mycorrespondingauthor}}
\fntext[mycorrespondingauthor]{abani@buffalo.edu}
%\cortext[mycorrespondingauthor]{abani@buffalo.edu}
%\ead{abani@buffalo.edu}
%\address[mymainaddress]{1600 John F Kennedy Boulevard, Philadelphia}
%\address[mysecondaryaddress]{360 Park Avenue South, New York}

@@

%\subsection{RSPH algorithm (the PESB algorithm)}
%The Godunov's method is summarized as a REA (reconstruct, evolve, average) algorithm. Here we summarize the RSPH algorithm as a PESB (project, evolve, sample, back-project) algorithm.
To summarize, our RSPH alogrithm proceeds as follows:
\begin{itemize}
\item For each pair of particles, establish a local coordinate system whose axis joins the
particles,
and project the primitive variables onto this local coordinate system to define
left and right states;
\item Solve this local Riemann problem approximately using a HLLC solver;
\item Sample the solution using the van der Corput sequence,
defining a state  $p^{\ast}, u^{\ast}$;
\item Project $p^{\ast}, u^{\ast}$  back to the global coordinate system,
to obtain $p^{\ast}$ and $\textbf{v}^{\ast}$;
\item Update the particle positions.
\end{itemize}

\section{Numerical tests} \label{numericaltests}
We carry out several numerical tests using SPH, RSPH and GSPH in this section.
1D shock tube tests are conducted to compare standard SPH, GSPH and RSPH. Comprehensive shock tube tests are also conducted to check the capacity of RSPH for different situations. In addition, order of accuracy is investigated based on 1D shock tube problem. 
In the last subsection, a 3D free jet flow is simulated with SPH, GSPH and RSPH to check equivalent overall dissipation introduced by each method.

Input parameters for 1D tests can be found in Table \ref{tab:1D-shock-input_parameters}. 
\begin{table}[htp]
\centering
      \caption{Overview of 1D shock tube tests}		
	  \begin{tabular}{lrrrrrrrrrr}
	    \hline
	          & $\rho_L$ & $p_L$ &$v_L$ & $\rho_R$ & $p_R$ &$v_R$ & $m$ & $[x_L, x_R]$ & $t_f$\\
	    \hline
	    Test 1 & $1.0$ & $1.0$ &$0$ & $0.25$ & $0.1795$ &$0$ & $0.003$  & $[-0.4, 0.4]$ & $0.17$\\
	    	Test 2 & $1.0$ & $1.0$ &$0$ & $0.5$ & $0.2$ &$0$ & $0.003$  & $[-0.4, 0.4]$ & $0.2$\\
	    	Test 3 & $2.0$ & $1.95$ &$1.0$ & $1.0$ & $1.95$ &$-1.0$  & $0.006$  & $[-0.4, 0.4]$ & $0.13$\\
	    Test 4 & $1.0$ & $2.4$ &$8.0$ & $0.5$ & $0.4$ &$-0.25$ & $0.003$  & $[-0.4, 0.4]$ & $0.05$\\
	    	Test 5 & $1.0$ & $-2.0$ &$0.4$ & $1.0$ & $0.4$ &$2.0$ & $0.003$  & $[-0.4, 0.4]$ & $0.18$\\
	    	Test 6 & $1.0$ & $0$ &$1000$ & $1.0$ & $0$ &$0.01$ & $0.003$  & $[-0.5, 0.5]$  & $0.01$\\
	    \hline
	  \end{tabular}
	  \label{tab:1D-shock-input_parameters}
\end{table}
where, subscript $L$ refers left side and $R$ for right side. $m$ is particle mass, initial interval between adjacent particles are adjusted to guarantee equal particle mass. $t_f$ is the time to terminate simulation and plotting the results. Equal particle mass is assigned to all particles. The $x$ axis in all plots is normalized by time, that is $x/t_f$, in plots for shock tube tests results.

Test 1 consists of a left rarefaction, a right travelling contact and a right shock. Density increases at down wind of contact wave.
Test 2 also consists of a left rarefaction, a right travelling contact and a right shock. Density decreases at down wind of contact wave.
Test 3 includes double expansion waves. The initial density are different at right and left hand side.
Test 4 is a double shock tests with different initial density on the right side and left side.
Test 5 and Test 6 are two extreme cases. Test 5 is a cavity flow while test 6 is a strong blast flow.

\subsection{Comparison of RSPH with standard SPH and GSPH}
\begin{figure}[htp]
    \centering
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-rho}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-v}
    \end{minipage}%
    \\
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-e}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-p}
    \end{minipage}% 
    \\
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-rho-zoom}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-v-zoom}
    \end{minipage}% 
    \\
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-e-zoom}
    \end{minipage}% 
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-p-zoom}
    \end{minipage}%    
    \caption{Simulation results by RSPH and SPH with different artificial viscosity coefficients. The effect of artificial viscosity is illustrated through comparison. Artificial viscosity coefficients are chosen to always satisfy: $\beta=2\alpha$ in all SPH tests. The last four figures are zoomed views. Almost no fluctuation is observed when $\alpha=1$ and $\alpha=2$, illustrating that numerical fluctuation is completely suppressed if artificial viscosity is large enough. For density distribution obtained by RSPH, the fluctuations are more obvious in the area away from shock than those calculated by SPH with $\alpha=0.2$, implying that RSPH introduces smaller artificial viscosity than SPH with $\alpha=0.2$ in the area far away from shock. However, fluctuations around shock is much more obvious for SPH with $\alpha=0.2$ than RSPH, implying that RSPH introduces larger artificial viscosity than ``$\alpha=0.2$" around shock. To summarize, the equivalent artificial viscosity in RSPH is adaptive. Similar conclusion can be drew from zoomed view of velocity. The third zoomed view shows different degrees of smearing at the shock. The larger the artificial viscosity, the less sharp the solution at the shock. Since ``$\alpha=0.2$" is sharper than ``RSPH" at the shock, ``$\alpha=0.2$" introduces less dissipation at the shock, which is consistent with information implied by zoomed view of density and velocity. SPH with $\alpha=1.0$ and $\alpha=2.0$ introduces more dissipation than ``RSPH" in the area around the shock. The last zoomed view shows pressure around the contact discontinuity. It shows that RSPH get rid of pressure ``wiggle" around the contact discontinuity.}
    \label{fig:RCM-Sod-SPH-alf}
\end{figure}

Test 1 is simulated using standard SPH with different artificial viscosity coefficients, GSPH and RSPH. The comparison between RSPH and SPH using different artificial viscosity coefficients is shown in Fig. \ref{fig:RCM-Sod-SPH-alf}. In all simulations, the artificial viscosity $\beta$ is set to be twice of $\alpha$. For example, for the test ``$SPH-\alpha=2$", $\beta=4$. Several interesting observation are made based on the comparison between SPH and RSPH.
First of all, dissipation (introduced by artificial viscosity in these tests) can decays the numerical fluctuations. Numerical fluctuations are suppressed completely when large enough dissipation is introduced, for example, by using sufficiently large artificial viscosity coefficients.
%The mechanism for SPH to reduce (or completely get rid of) fluctuations should be completely different from that of new adaptive method of smoothing length. 
%The new adaptive method, reduces the sources of such fluctuations.
Secondly, the equivalent artificial viscosity coefficients introduced by RSPH varies adaptively.
As shown in Fig. \ref{fig:RCM-Sod-SPH-alf}, RSPH assigns smaller artificial viscosity coefficients (equivalent $\alpha$ much less then 0.2) at the area far away from shock and sufficient large artificial viscosity coefficients (equivalent $\alpha$ is about 1.0) around the shock. So RSPH is actually more adaptive than SPH. This feature is very desirable not only because it could eliminate parameterization and hence user intervention associated with artificial viscosity coefficients but also because it avoids introducing excessive artificial viscosity when unnecessary.
Thirdly, RSPH introduces less smearing of the shock discontinuity compared with SPH using most commonly adopted artificial viscosity coefficients ($\alpha=1.0$, $\beta=2.0$). Recall that RCM is able to resolve discontinuities as true discontinuity. RSPH, even though still smears the discontinuity in some degree, introduces much less smearing.
The last but not the least, the pressure ``wiggle" around contact discontinuity is completely eliminated by RSPH. It has been shown that thermal conduction is essential to mitigate the spurious pressure ``wiggle" at contact discontinuity in SPH \citep{monaghan1997sph, sigalotti2006shock, price2008modelling, price2012smoothed}. As for GSPH, it is reported that an implicit thermal conduction is introduced by Godunov's scheme and help suppress the anomaly \citep{puri2014approximate}. Even though, the ``wiggle" still visible in pressure distribution and velocity distribution of GSPH simulation results (for example, see figures in \citep{puri2014comparison}) and RSPH simulation results of other tests (see section \ref{sec:comprehensive-1d-tests}). ``Wiggle" in test 1, however, is completely eliminated by both GSPH and RSPH.

\begin{figure}[htp]
    \centering
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-rho}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-v}
    \end{minipage}%
    \\
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-e}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-p}
    \end{minipage}% 
    \\
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-rho-zoom}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-e-zoom}
    \end{minipage}% 
    \\
    \begin{minipage}{.495 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-v-zoom}
    \end{minipage}% 
    \begin{minipage}{.495\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-GSPH-compare-p-zoom}
    \end{minipage}%    
    \caption{Comparison of RSPH with GSPH using Roe Riemann solver and HLLC Riemann solver. The last four plots are zoomed views. Zoomed view of density and specific internal energy show that GSPH smears the discontinuity at shock much more than RSPH. Zoomed view of velocity shows that fluctuation in GSPH is completely suppressed, which implies that numerical dissipation introduced in GSPH is at least around the same amount as SPH with $\alpha=1.0$. This is consistent with information implied by zoomed view of density and specific internal energy. The last zoomed view shows that both RSPH and GSPH can get rid of pressure ``wiggle" around the contact discontinuity.}
    \label{fig:RCM-Sod-GSPH}
\end{figure}

These zoomed views in fig. \ref{fig:RCM-Sod-GSPH} demonstrate that RSPH introduces less but sufficient dissipation compared with GSPH. The attractive feature of RCM method in preserving true discontinuity is inherited by RSPH in this 1D shock tube test. With more dissipation, GSPH can completely suppress numerical dissipation. The discontinuity at the shock is more seriously smeared. The excessive amount dissipation might have other, more undesirable, effects in real implementation. For example, over damping of shearing flow. Compared with SPH, both GSPH and RSPH avoid pressure ``wiggle" around contact discontinuity. Since RSPH share many common places with Godunov's method, it is not surprise that RSPH can also suppress the pressure ``wiggle" at contact discontinuity.

\subsection{Accuracy tests}
We use shock tube test to gauge the accuracy of the RSPH scheme.
% for both situations when the solution remains smooth and when there are shocks in the solution. We use test 1 to conduct order of accuracy test for the case with shocks in the solution. 
We examine the errors between simulation results and the analytical solution (the reference solution) as the number of particles is increased. The $L_1$ norm error, defined for a property $f$, is normalized by the number of particles as:
\begin{equation}
L_1= \frac{1}{N_p} \sum_a^{N_p} \vert f_a^{SPH} - f^{REF} (x_a) \vert 
\end{equation}
where the superscript $REF$ represent the reference solution, $SPH$ represents simulation results calculated by different SPH schemes. Fig. \ref{fig:Accuracy-test1} displays the $L_1$ norm errors for the density, velocity and pressure profiles for different SPH schemes.
We observe a rate of convergence of approximately 1 for GSPH and 1.5 for standard SPH and RSPH.
GSPH with an exact Riemann solver has been shown to be approximately second order of accuracy \citep{puri2014comparison} and comparable in accuracy to the standard SPH schemes when using piece wise linear construction. As for GSPH using approximate Riemann solver, \citet{puri2014approximate} reported second order accuracy for HLLC and Roe Riemann solvers adopting piece wise linear Riemann problem construction. In addition, they adopted a test problem without discontinuity in the solution. Existing of discontinuities, such as shock, in the test problem might lower rate of convergence. Both RSPH and GSPH tests in this paper adopt a piece wise constant construction of Riemann problem. So we conclude that RSPH shows higher order of accuracy than GSPH when using the same Riemann problem construction. Compared with SPH, RSPH shows almost the same order of accuracy and level of error.
%It is worthwhile to check the order of accuracy of GSPH using piecewise linear constructor
%It is also worthwile to check what of order of accuracy using another test problem.  
\begin{figure}[H]
    \centering
    \begin{minipage}{.332\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Accuracy-des}
    \end{minipage}%
    \begin{minipage}{.332 \textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Accuracy-vel}
    \end{minipage}%
    \begin{minipage}{.332\textwidth}
        \centering
        \includegraphics[width=0.99 \textwidth]{./Figures/Accuracy-pre}
    \end{minipage}%  
    \caption{ $L_1$ norm errors for 1D shock tube test (test1) for RSPH, standard SPH, GSPH using Roe Riemann solver and GSPH using HLLC Riemann Solver.  GSPH with the HLLC approximate Riemann solver exhibits the same convergence rate (around 1) but quantitatively larger errors than that with Roe Riemann solver. RSPH and standard SPH shows same rate of convergence and almost same amount of error.}
    \label{fig:Accuracy-test1}
\end{figure}

>>>>

\modulolinenumbers[5]
\journal{Journal of Computational Physics}
%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%
%% Numbered
\bibliographystyle{model1-num-names}
%% Numbered without titles
%\bibliographystyle{model1a-num-names}
%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}
%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}
%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}
%% `Elsevier LaTeX' style
%\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{frontmatter}
\title{A Random Choice SPH Scheme with Adaptive Viscosity}
%\tnotetext[mytitlenote]{Can add  title note here}
%% Group authors per affiliation:
\author{Zhixuan Cao}
\author{Abani Patra \fnref{mycorrespondingauthor}}
\address{Department of Mechanical and Aerospace Engineering,The State University of New York at Buffalo, Amherst, NY, 14260-4200, USA}
\author{E. Bruce Pitman}
\address{Department of Materials Design and Innovation, The State University of New York at Buffalo, Amherst, NY, 14260-4200, USA}
%\fntext[myfootnote]{Since 1880.}
%% or include affiliations in footnotes:
%\author[mymainaddress,mysecondaryaddress]%{Elsevier Inc}
%\ead[url]{www.elsevier.com}
%\author[mysecondaryaddress]{Global Customer Service\corref{mycorrespondingauthor}}
\fntext[mycorrespondingauthor]{abani@buffalo.edu}
%\cortext[mycorrespondingauthor]{abani@buffalo.edu}
%\ead{abani@buffalo.edu}
%\address[mymainaddress]{1600 John F Kennedy Boulevard, Philadelphia}
%\address[mysecondaryaddress]{360 Park Avenue South, New York}

@@

%\subsection{RSPH algorithm (the PESB algorithm)}
%The Godunov's method is summarized as a REA (reconstruct, evolve, average) algorithm. Here we summarize the RSPH algorithm as a PESB (project, evolve, sample, back-project) algorithm.
To summarize, our RSPH algorithm proceeds as follows:
\begin{itemize}
\item For each pair of particles, establish a local coordinate system whose axis joins the
particles,
and project the primitive variables onto this local coordinate system to define
left and right states;
\item Solve this local Riemann problem approximately using a HLLC solver;
\item Sample the solution using the van der Corput sequence,
defining a state  $p^{\ast}, u^{\ast}$;
\item Project $p^{\ast}, u^{\ast}$  back to the global coordinate system,
to obtain $p^{\ast}$ and $\textbf{v}^{\ast}$;
\item Update the particle positions.
\end{itemize}

\section{Numerical tests} \label{numericaltests}
We describe results from several numerical tests using SPH, RSPH and GSPH in this section.
1D shock tube tests are used to compare standard SPH, GSPH and RSPH. Comprehensive shock tube simulations are also conducted to check the capacity of RSPH for different situations. In addition, order of accuracy is investigated for the 1D shock tube problem. 
In the last subsection we describe a 3D free jet flow simulation with SPH, GSPH and RSPH to check equivalent overall dissipation introduced by each method.

Six 1D simulations described here  are carried out:
\begin{itemize}% [1D Tests]
\item Test 1 consists of a left rarefaction, a right traveling contact and a right shock. Density increases at down wind of contact wave. 
\item Test 2 also consists of a left rarefaction, a right traveling contact and a right shock. Density decreases at down wind of contact wave. 
\item Test 3 includes double expansion waves. The initial density are different at right and left hand side. 
\item Test 4 is a double shock tests with different initial density on the right side and left side.
\item Test 5 and Test 6 are two extreme cases. Test 5 is a cavity flow while test 6 is a strong blast flow.
\end{itemize}

\begin{table}[htp]
\centering
      \caption{Overview of 1D shock tube tests}		
	  \begin{tabular}{lrrrrrrrrrr}
	    \hline
	          & $\rho_L$ & $p_L$ &$v_L$ & $\rho_R$ & $p_R$ &$v_R$ & $m$ & $[x_L, x_R]$ & $t_f$\\
	    \hline
	    Test 1 & $1.0$ & $1.0$ &$0$ & $0.25$ & $0.1795$ &$0$ & $0.003$  & $[-0.4, 0.4]$ & $0.17$\\
	    	Test 2 & $1.0$ & $1.0$ &$0$ & $0.5$ & $0.2$ &$0$ & $0.003$  & $[-0.4, 0.4]$ & $0.2$\\
	    	Test 3 & $2.0$ & $1.95$ &$1.0$ & $1.0$ & $1.95$ &$-1.0$  & $0.006$  & $[-0.4, 0.4]$ & $0.13$\\
	    Test 4 & $1.0$ & $2.4$ &$8.0$ & $0.5$ & $0.4$ &$-0.25$ & $0.003$  & $[-0.4, 0.4]$ & $0.05$\\
	    	Test 5 & $1.0$ & $-2.0$ &$0.4$ & $1.0$ & $0.4$ &$2.0$ & $0.003$  & $[-0.4, 0.4]$ & $0.18$\\
	    	Test 6 & $1.0$ & $0$ &$1000$ & $1.0$ & $0$ &$0.01$ & $0.003$  & $[-0.5, 0.5]$  & $0.01$\\
	    \hline
	  \end{tabular}
	  \label{tab:1D-shock-input_parameters}
\end{table}
Input parameters for 1D tests can be found in Table \ref{tab:1D-shock-input_parameters}, where, subscript $L$ refers left side and $R$ for right side. $m$ is particle mass, initial interval between adjacent particles are adjusted to guarantee equal particle mass. $t_f$ is the time to terminate simulation and plotting the results. Equal particle mass is assigned to all particles. The $x$ axis in all plots is normalized by time, that is $x/t_f$, in plots for shock tube tests results.
\subsection{Comparison of RSPH with standard SPH and GSPH}
\begin{figure}[htp]
    \centering
    \begin{minipage}{.495\textwidth}
        \centering a)
        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-rho}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering b)
        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-v}
    \end{minipage}%
%    \\
%    \begin{minipage}{.495\textwidth}
%        \centering c)
%        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-e}
%    \end{minipage}%
%    \begin{minipage}{.495 \textwidth}
%        \centering d)
%        \includegraphics[width=0.99 \textwidth,height=0.6\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-p}
%    \end{minipage}% 
    \\
    \begin{minipage}{.495\textwidth}
        \centering c)
        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-rho-zoom}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering d)
        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-v-zoom}
    \end{minipage}% 
%    \\
%    \begin{minipage}{.495 \textwidth}
%        \centering g)
%        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-e-zoom}
%    \end{minipage}% 
%    \begin{minipage}{.495\textwidth}
%        \centering h)
%        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-p-zoom}
%    \end{minipage}%    
    \caption{a),b) Simulation results of density and velocity in Test 1 by RSPH and SPH with different artificial viscosity coefficients $\alpha,\beta$ satisfying: $\beta=2\alpha$.  c), d) show zoomed views.  For $\alpha=1$ and $\alpha=2$,numerical oscillations are completely suppressed though the shock is now smeared. $\alpha=0.25$ provided insufficient viscosity to suppress oscillations. Comparing  RSPH and SPH shows that RSPH is adaptive and more dissipative at the shock 
    (comparable to $\alpha=1.0$ and $\alpha=2.0$) and less dissipative away from the shock (comparable to $\alpha=0.25$). %    
%    
%    For density distribution obtained by RSPH, the fluctuations are more obvious in the area away from shock than those calculated by SPH with $\alpha=0.2$, implying that RSPH introduces smaller artificial viscosity than SPH with $\alpha=0.2$ in the area far away from shock. However, fluctuations around shock is much more obvious for SPH with $\alpha=0.2$ than RSPH, implying that RSPH introduces larger artificial viscosity than ``$\alpha=0.2$" around shock. To summarize, the equivalent artificial viscosity in RSPH is adaptive. Similar conclusion can be drew from zoomed view of velocity. The third zoomed view shows different degrees of smearing at the shock. The larger the artificial viscosity, the less sharp the solution at the shock. Since ``$\alpha=0.2$" is sharper than ``RSPH" at the shock, ``$\alpha=0.2$" introduces less dissipation at the shock, which is consistent with information implied by zoomed view of density and velocity. SPH with $\alpha=1.0$ and $\alpha=2.0$ introduces more dissipation than ``RSPH" in the area around the shock. The last zoomed view shows pressure around the contact discontinuity. It shows that RSPH get rid of pressure ``wiggle" around the contact discontinuity.
    }
    \label{fig:RCM-Sod-SPH-alf}
\end{figure}

\begin{figure}[htp]
    \centering
%    \begin{minipage}{.495\textwidth}
%        \centering a)
%        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-rho}
%    \end{minipage}%
%    \begin{minipage}{.495 \textwidth}
%        \centering b)
%        \includegraphics[width=0.99 \textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-v}
%    \end{minipage}%
%    \\
    \begin{minipage}{.495\textwidth}
        \centering a)
        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-e}
    \end{minipage}%
    \begin{minipage}{.495 \textwidth}
        \centering b)
        \includegraphics[width=0.99 \textwidth,height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-p}
    \end{minipage}% 
    \\
%    \begin{minipage}{.495\textwidth}
%        \centering a)
%        \includegraphics[width=0.99 \textwidth, height=0.6\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-rho-zoom}
%    \end{minipage}%
%    \begin{minipage}{.495 \textwidth}
%        \centering b)
%        \includegraphics[width=0.99 \textwidth, height=0.6\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-v-zoom}
%    \end{minipage}% 
%    \\
    \begin{minipage}{.495 \textwidth}
        \centering c)
        \includegraphics[width=0.99 \textwidth, height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-e-zoom}
    \end{minipage}% 
    \begin{minipage}{.495\textwidth}
        \centering d)
        \includegraphics[width=0.99 \textwidth, height=0.7\textwidth]{./Figures/Sod/RCM-Sod-SPH-alf-p-zoom}
    \end{minipage}%    
    \caption{
    a),b) Simulation results of internal energy and pressure in Test 1 by RSPH and SPH with different artificial viscosity coefficients $\alpha,\beta$ satisfying: $\beta=2\alpha$.  c), d) show zoomed views.  For $\alpha=1$ and $\alpha=2$,numerical oscillations are completely suppressed though the shock is now smeared. $\alpha=0.25$ provided insufficient viscosity to suppress oscillations. Comparing  RSPH and SPH shows that RSPH is adaptive and more dissipative at the shock 
    (comparable or better than $\alpha=1.0$ and $\alpha=2.0$) and less dissipative away from the shock (comparable to $\alpha=0.25$). d) shows pressure around the contact discontinuity. It shows that RSPH gets rid of the pressure ``wiggle" around the contact discontinuity.
%
%    Simulation results by RSPH and SPH with different artificial viscosity coefficients $\alpha,\beta$ satisfying: $\beta=2\alpha$. The last four figures are zoomed views. Almost no fluctuation is observed when $\alpha=1$ and $\alpha=2$, illustrating that numerical fluctuation is completely suppressed if artificial viscosity is large enough. For density distribution obtained by RSPH, the fluctuations are more obvious in the area away from shock than those calculated by SPH with $\alpha=0.2$, implying that RSPH introduces smaller artificial viscosity than SPH with $\alpha=0.2$ in the area far away from shock. However, fluctuations around shock is much more obvious for SPH with $\alpha=0.2$ than RSPH, implying that RSPH introduces larger artificial viscosity than ``$\alpha=0.2$" around shock. To summarize, the equivalent artificial viscosity in RSPH is adaptive. Similar conclusion can be drew from zoomed view of velocity. The third zoomed view shows different degrees of smearing at the shock. The larger the artificial viscosity, the less sharp the solution at the shock. Since ``$\alpha=0.2$" is sharper than ``RSPH" at the shock, ``$\alpha=0.2$" introduces less dissipation at the shock, which is consistent with information implied by zoomed view of density and velocity. SPH with $\alpha=1.0$ and $\alpha=2.0$ introduces more dissipation than ``RSPH" in the area around the shock. The last zoomed view shows pressure around the contact discontinuity. It shows that RSPH get rid of pressure ``wiggle" around the contact discontinuity.
}
    \label{fig:RCM-Sod-SPH-alf-zoom}
\end{figure}

Test 1 is simulated using standard SPH with different artificial viscosity coefficients, GSPH and RSPH. The comparison between RSPH and SPH using different artificial viscosity coefficients is shown in Fig. \ref{fig:RCM-Sod-SPH-alf} and \ref{fig:RCM-Sod-SPH-alf-zoom}. In all simulations, the artificial viscosity $\beta$ is set to be twice of $\alpha$. For example, for the test ``$SPH-\alpha=2$", $\beta=4$. Several interesting observation are made based on the comparison between SPH and RSPH. The effect of artificial viscosity is illustrated through comparison.
First of all, dissipation (introduced by artificial viscosity in these tests) decays the numerical fluctuations. Numerical fluctuations are suppressed completely when large enough dissipation is introduced, for example, by using sufficiently large artificial viscosity coefficients ($\alpha=1,2$).
%The mechanism for SPH to reduce (or completely get rid of) fluctuations should be completely different from that of new adaptive method of smoothing length. 
%The new adaptive method, reduces the sources of such fluctuations.
Secondly, the equivalent artificial viscosity  introduced by RSPH varies adaptively.
As shown in Fig. \ref{fig:RCM-Sod-SPH-alf} and \ref{fig:RCM-Sod-SPH-alf-zoom}, RSPH assigns smaller artificial viscosity  (equivalent $\alpha$ much less then 0.2) at the area far away from shock and sufficiently large artificial viscosity coefficients (equivalent $\alpha$ is about 1.0) around the shock. So RSPH is actually more adaptive than SPH. This feature is very desirable not only because it could eliminate parameterization and hence user intervention associated with artificial viscosity coefficients but also because it avoids introducing excessive artificial viscosity when unnecessary.
Thirdly, RSPH introduces less smearing of the shock discontinuity compared with SPH using most commonly adopted artificial viscosity coefficients ($\alpha=1.0$, $\beta=2.0$). Recall that RCM is able to resolve discontinuities as true discontinuity. RSPH, even though it still smears the discontinuity in some degree, introduces much less smearing.
The last but not the least, the pressure ``wiggle" around contact discontinuity is completely eliminated by RSPH as seen in Fig. \ref{fig:RCM-Sod-SPH-alf-zoom}. It has been shown that thermal conduction is essential to mitigate the spurious pressure ``wiggle" at contact discontinuity in SPH \citep{monaghan1997sph, sigalotti2006shock, price2008modelling, price2012smoothed}. As for GSPH, it is reported that an implicit thermal conduction is introduced by Godunov's scheme and help suppress the anomaly \citep{puri2014approximate}. Even though, the ``wiggle" still visible in pressure distribution and velocity distribution of GSPH simulation results (for example, see figures in \citep{puri2014comparison}) and RSPH simulation results of other tests (see section \ref{sec:comprehensive-1d-tests}). ``Wiggle" in test 1, however, is completely eliminated by both GSPH and RSPH.
